---
title: "Project 3: mypracticepackage Tutorial"
author: "Andrew Lee & Lori Wang"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mypracticepackage Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
### Introduction
This package features many statistical functions developed by me for the STAT 302 class at the University of Washington. It can be installed via the following code:
```{r, eval = FALSE}
devtools::install_github("andrewl916/mypracticepackage", build_vignette = TRUE, build_opts = c())
```

```{r setup}
library(magrittr)
library(dplyr)
library(mypracticepackage)
library(kableExtra)
library(ggplot2)
library(class)
library(randomForest)

penguins <- read.csv("C:/Users/andre/Desktop/STAT302/projects/project_3/ProjectPipelinePackage/Data/my_penguins.csv")

source("C:/Users/andre/Desktop/STAT302/projects/project_3/mypracticepackage/R/my_rf_cv.R")
```

### my_rf_cv Demonstration
Instead of classifying based on neighboring data points in the training data,
the random forest algorithm classify based on splits in the parameters.
We want to predict $$body\_mass\_g$$ using covariates $$bill\_length\_mm$$, $$bill\_depth\_mm$$, $$flipper\_length\_mm$$.
Inputs:
- \code{k}: number of folds
```{r}
# remove NA data in the data set
penguins <- na.omit(penguins)

# create a list to label the number of folds
folds <- c(rep("2", 30), rep("5", 30), rep("10", 30))

# create empty lists to store MSE
MSE_2 <- rep(NA, length(30))
MSE_5 <- rep(NA, length(30))
MSE_10 <- rep(NA, length(30))

# fill MSE data
for (k in 1:30){
  MSE_2[k] <- my_rf_cv(2)
  MSE_5[k] <- my_rf_cv(5)
  MSE_10[k] <- my_rf_cv(10)
}

# combine the label and data into one data frame
MSE_data <- data.frame(names = folds,
                       MSE = c(MSE_2, MSE_5, MSE_10))
```
```{r, fig.width=10,fig.height=11}
# plot the data
ggplot(data = MSE_data,
       aes(x = names, MSE)) +
  geom_boxplot(fill = "lightblue") +
  theme_bw(base_size = 20) +
  labs(title = "MSE According to Number of Folds",
       x = "Number of Folds",
       y = "MSE") +
  theme(plot.title =
          element_text(hjust = 0.5),
        text = element_text(size = 12)) +
  ggsave(filename = "../Output/Figures/mse_boxplot.png")
```
```{r}
MSE_table <- data.frame("folds" = c(2, 5, 10),
                        "mean" = c(mean(MSE_2), mean(MSE_5), mean(MSE_10)),
                        "std_deviation" = c(sd(MSE_2), sd(MSE_5), sd(MSE_10)))
kable_styling(kable(MSE_table))

write.csv(MSE_data, "../Output/Results/MSE_data.csv")
saveRDS(MSE_table, "../Output/Results/MSE_table.RDS")
```
In general, a fold of 2 has the widest standard deviation, while a fold of 10 gives the lowest mean MSE. THis could be the case because having 10 folds allows for the algorithm to best predict the body weight of the penguins in the dataset.
